---
title: "Exploratory Analysis"
author: "Group 2: Sonali Chandra, John-Luke Dokupil, Samantha Chow"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
```

## Distribution Graphics

```{r, echo = FALSE, warning = FALSE}
box_plot
```

#### Analysis for Average Number of People with Any Mental Illness based on Ethnicity
This graph shows the number of people who have reported any occurrence of mental illness, based on age group and ethnicity. The points shown on the graph are organized by age group, and show the exact number of people who have had any mental illness, where the ethnicity groupings are based on colors. The box plots display an average count across all the age groups, and the ethnicities are also represented by colors. From this graph, there are a high number of people who are White that have mental illness compared to the other ethnicities, and this could be an indication of the amount of health care access that everyone has. The dramatic difference between this ethnicity and the other ones shown could be because of the imbalance of representation from the data collected, or maybe the willingness to admit mental illness or disclose sensitive health information.


## Relationship Graphics

```{r, echo = FALSE, warning = FALSE}
line_plot
```

#### Analysis for Recorded Presence of Mental Illness Among People 18 Years or Older
This graph shows the number of people over 18 years old who experienced mental illness over the years of 2008 to 2018. As the data is shown based on the county type, it seems that a lot more people who live in larger cities experience mental illness, and this could be dependent on the stresses that come along with living in larger urban areas. However, the data could be skewing this way because those who live in smaller counties, where they are completely urban or non metropolitan could be not accurately represented by this graph because they did not have access to record mental illness or a way to address these concerns with help due to their remote locations. 

