---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
source("distribution.R")
```

```{r, echo = FALSE, warning = FALSE}
any
```


```{r, echo = FALSE, warning = FALSE}
received
```

#### Analysis for Bar Plot
These graphs show the number of people (in thousands) over 18 years old who have any mental illnesses compared to
those who had received mental health services in 2017 and 2018 combined. Any refers to any mental illnesses reported,
Serious refers to serious mental illnesses reported, Excluding reders to any mental illnesses excluding serious mental illnesses, and None refers to those with no mental illnesses recorded.
The dataset was filtered through geographic/socioeconomic characteristics, so we
chose to look at the relationship between education levels and those getting mental health help in the US. 
The graphs generally show that more people reported mental illnesses than the amount of people getting
help, but we can see that those with college or associates degrees have the largest amount of mental illnesses, yet
they're the group with the most number of people that got help. We can also use this data by mapping it out
and comparing it to areas of the US with high and low education levels to make inferences about where access to mental 
health services are the highest and lowest.

